### 2025-09-08 submissions/03-jpam-RR/manuscript_main.tex
add new plots and from the data section
add sectiion and start working on it

While CPS relies on household respondents (parents or caregivers) to report children's racial identity, this proxy reporting likely reflects children's actual identity since parents significantly influence identity formation. \textcite{duncanIntermarriageIntergenerationalTransmission2011} support this perspective, demonstrating no variation in Asian identification based on household respondent type. The data confirms consistent Asian identity reporting regardless of whether mother (72\%), father (72\%), or child/other caregiver (87\%) serves as respondent, as shown in Table \ref{tab:hispbyproxy}.\footnote{According to CPS guidelines, household respondents must be at least 15 years old with sufficient household knowledge. When the proxy is `self,' the respondent ranges from 15 to 17 years old.} Since my analysis compares high and low bias states, estimates remain valid provided reporting patterns don't systematically differ between these contexts. Furthermore, ethnic attrition patterns among adults align with those observed in children, as shown in Table (\ref{tab:hispbygen-adults}), suggesting that proxy reporting aligns with individuals' self-identification.

@@

My analysis employs a US population subsample; Table (\ref{tab:hispbygen}) demonstrates sufficient observations across generations. Consistent with literature on racial identity fluidity among Asian Americans, I document significant attrition among third-generation Asian Americans.\footnote{\textcite{duncanIdentifyingLaterGenerationDescendants2018,duncanSocioeconomicIntegrationImmigrant2018, antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020} document substantial identity attrition among various groups.} Table (\ref{tab:hispbygen}) displays these patterns: most first- and second-generation Asian Americans racially self-identify as Asian. Among first-generation Asian Americans, 96\% self-report Asian racial identity. Among second-generation Asian Americans, 73\% self-identify as Asian, while 31\% of third-generation Asian Americans choose Asian racial identification. Attrition among second- and third-generation Asian Americans primarily occurs among children from interracial families. The pattern among adults---see Table (\ref{tab:hispbygen-adults})---is similar, with 96\% of first-generation and 73\% of second-generation Asian Americans self-identifying as Asian. Breaking down by interracial families, second-generation Asian Americans with Asian parents report 95\% Asian identification, while those with one Asian and one White parent report 37\% Asian identification.

@@

>>>>

While CPS relies on household respondents (parents or caregivers) to report children's racial identity, this proxy reporting likely reflects children's actual identity since parents significantly influence identity formation. \textcite{duncanIntermarriageIntergenerationalTransmission2011} support this perspective, demonstrating no variation in Asian identification based on household respondent type. The data confirms consistent Asian identity reporting regardless of whether mother (72\%), father (72\%), or child/other caregiver (87\%) serves as respondent, as shown in Table \ref{tab:hispbyproxy}.\footnote{According to CPS guidelines, household respondents must be at least 15 years old with sufficient household knowledge. When the proxy is `self,' the respondent ranges from 15 to 17 years old.} Since my analysis compares high and low bias states, estimates remain valid provided reporting patterns don't systematically differ between these contexts.

@@

My analysis employs a US population subsample; Table (\ref{tab:hispbygen}) demonstrates sufficient observations across generations. Consistent with literature on racial identity fluidity among Asian Americans, I document significant attrition among third-generation Asian Americans.\footnote{\textcite{duncanIdentifyingLaterGenerationDescendants2018,duncanSocioeconomicIntegrationImmigrant2018, antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020} document substantial identity attrition among various groups.} Furthermore, ethnic attrition patterns among adults align with those observed in children, as shown in Table (\ref{tab:hispbygen-adults}), suggesting that proxy reporting aligns with individuals' self-identification.

@@

\section{From the Data: Asian Racial Identity and Attrition}\label{sec:attrition}

\subsection{Asian Racial Identity Attrition by Generation and Family Structure}

In this section, I document Asian racial identity reporting patterns and attrition across generations. First, I show that Asian racial identity attrition by generation for both children and adult samples. Second, I examine which racial identities individuals with objective Asian ancestry report (Asian, White, multiracial, etc.), presenting results for children broken down by generation and family structure (interracial versus endogamous parents).

Table (\ref{tab:hispbygen}) displays the pattern of racial attrition. Most first- and second-generation Asian Americans racially self-identify as Asian. Among first-generation Asian Americans, 96\% self-report Asian racial identity displaying weak racial attrition. Among second-generation Asian Americans, 73\% self-identify as Asian, while 31\% of third-generation Asian Americans choose Asian racial identification. Attrition among second- and third-generation Asian Americans primarily occurs among children from interracial families. Interracial second-generation Asian Americans with one Asian and one White parent report 33\% Asian identification, while those with two Asian parents report 97\% Asian identification. Among third-generation Asian Americans, 25\% report Asian identification, with 94\% of those with four Asian grandparents reporting Asian identification. Therefore, Asian racial identity attrition is substantial, driven mainly by children from interracial families.

I show the pattern among adults in Table (\ref{tab:hispbygen-adults}). Since I cannot observe the birth places of grandparents among the adult sample, I show the pattern of Asian racial identity among first- and second-generation adults. Among first-generation Asian adults, 96\% self-identify as Asian. Among second-generation native-born Asian individuals 73\%  self-identify as Asian. Breaking down by interracial families, second-generation Asian Americans with Asian parents report 95\% Asian identification, while those with one Asian and one White parent report 37\% Asian identification. Thus, the first- and second-generation Asian adult samples exhibit similar patterns to the child sample.

\subsection{Racial Identity Choices Among Those with Asian Ancestry}
I display racial identity choices among objectively Asian children by generation in Figures \ref{fig:histogram-all}-\ref{fig:histogram-thirdgen}. The figures show the distribution of racial identity choices among objectively Asian children, broken down by generation, and family structure (interracial versus endogamous parents). The figures reveal that while most first-generation Asian children identify as Asian, a significant portion of second- and third-generation children choose other racial identities, particularly those from interracial families. This highlights the complexity of racial identity formation and the influence of family structure on identity choices.
